\begin{acknowledgements}

I would like to thank my supervisor, Prof.~Phil Torr, for having faith in me and providing the opportunity to pursue a PhD.
His infectious energy and creativity have been pivotal in making this thesis possible.

I have also had the pleasure of working closely with many collaborators during my PhD. 
My mentors in my initial projects -- Michael, Ondra, Stuart and Sadeep -- have played a significant role in my development as a researcher.
I have also enjoyed subsequent collaborations with Kyle, Qizhu, M{\aa}ns, Fredrik, Li, Rodrigo and Carl.
Further thanks go to the computer vision teams in DeepMind and Google (particularly Abhanshu, Matt and Sammy) for hosting me. %during two \FIX{unforgettable} summers.
Bernardino and Stuart have also taken the time to provide detailed and thoughtful feedback on drafts of my papers on numerous occasions.

I have been fortunate to be part of the computer vision community in Oxford.
There are too many past and present members in TVG to name here, along with many others from VGG, OVAL and AVL from whom I have learned things from whilst sharing an ``office''.
One of the best perks of studying at Oxford has been the impressive array of seminar speakers who have given talks here and then been available for further discussions afterwards.
%Another advantage of the large research community at Oxford has been the impressive array of seminar speakers who have visited and given talks here.
I am also grateful to my transfer report examiners, Professors Pawan Kumar and Paul Newman, and also Prof.~Andrew Zissermann whom I collaborated with.
My thesis examiners, Professors Andrea Vedaldi and Iasonas Kokkinos, also provided insightful comments on the manuscript and the viva itself turned out to be a stimulating discussion.

\iffalse
Furthermore, it has been a priviledge to regularly have 

 have a steady stream of invited seminar speakers, and 

, -- there are too many past and present members in TVG to name here, along with many other

-- multiple reserach groups
-- top speakers
	-- In both cases, I have learned cool stuff from them.
	-- had good audience questions
-- transfer report, AZ
	
I have been fortunate to be part of the computer vision community in Oxford, with its impressive array of invited seminar speakers, and filled with many great minds from whom I have learned a lot from.
There are too many past and present members in TVG to name here, along with many others from VGG, OVAL and AVL.
I am also grateful to my transfer report examiners, Professors Pawan Kumar and Paul Newman, and also Prof. Andrew Zisserman whom I collaborated with and learned a lot from.
\fi

I have thoroughly enjoyed my time here in Oxford, both inside and outside of the lab, thanks to Sven, Aravindh, Namhoon, Jessamy, Qizhu, Li, Arnab, Harkirat, Daniela, Oscar, Piotr, Vivek and the badminton clubs of Linacre and Jesus College.

Maddy, and then later Cassandra, have also been helpful regarding all administrative matters.
And thanks to Jerry, as well as the ARC team, for managing the group's computing resources.

I am grateful to my family for their continual support during my PhD. In particular, I am thankful to Didi for proof-reading yet another thesis and spoiling me on every vacation.

Finally, I am grateful to have been funded by the Clarendon Scholarship.

\iffalse
I have also had the pleasure of working closely with 

I have been fortunate to be part of the Torr Vision Group, filled with many great minds from whom I have learned a lot from.
Furthermore


I have been fortunate to be part of the computer vision community in Oxford 

I have been fortunate to be part of the Torr Vision Group, filled with many great minds from whom I have learned a lot from.
	
I would like to thank my supervisor, Prof. Phil Torr, for having faith in me and providing the opportunity to pursue a PhD.
Phil's infectious passion, energy and creativity 
% and willingness to support my work even when he did not agree with it
has been pivotal in making this thesis possible.

I have been fortunate to be part of the Torr Vision Group 

for having faith in me, giving me a chance, supporting me even when I went against his wishes,	
	
Phil passion and creativity

Transfer report examiners, Professors Pawan Kumar and Paul Newman.
Also fortunate to work with Andrew Zisserman.

Collaborators: early on: Michael, Ondra, Stuart, Sadeep
More collaborators: Kyle, Mans, Fredrick, Qizhu, Carl

AZ, Carl at DeepMind, Abhanshu, Sammy and Matt at Google

Lab at Oxford -- TVG, Oval and VGG enriching experience.
Great speakers at seminars

Social: Namhoon, Qizhu, Li, Arnab, Harkirat, Daniela
Sven, Jessamy

Bernardino and Stuart for feedback on my papers.

Clarendon Scholarship, for supporting my DPhil studies.
Maddy, Cassandra and Lincare College for all adminstrative queries

Family for support. In particular, Didi, for proof-reading yet another thesis and spoiling me on vacations.
\fi

\end{acknowledgements}